---
title: "R Notebook"
output: html_notebook
---


```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("prada")

```


```{r}
source("https://bioconductor.org/biocLite.R")
biocLite("facsDorit")
```


```{r}
library("prada")
 library("facsDorit")'
```


```{r}


+
+
> viab[1:2, ]
> > +
rg <- 1000 * c(250, 2000)
boxplot(log(Kc1) ~ Plate384, data = viab, outline = FALSE,
    col = "#A6CEE3", ylim = log(rg))
viab <- read.table(system.file("extdata", "BoutrosKiger.tab", package = "facsDorit"), header = TRUE, as.is = TRUE,
sep = "\t")

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

