---
title: "R Notebook"
output: html_notebook
---
```{r}
# NOT RUN {
(ff <- factor(substring("statistics", 1:10, 1:10), levels = letters))
```


```{r}
as.integer(ff)      # the internal codes
```


```{r}
# drops the levels that do not occur
(f. <- factor(ff))


# the same, more transparently
ff[, drop = TRUE]  
```
```{r}
factor(letters[1:20], labels = "letter")
```


```{r}
class(ordered(4:1)) # "ordered", inheriting from "factor"
```


```{r}
z <- factor(LETTERS[3:1], ordered = TRUE)
## and "relational" methods work:
stopifnot(sort(z)[c(1,3)] == range(z), min(z) < max(z))
# }
```


```{r}
# NOT RUN {
## suppose you want "NA" as a level, and to allow missing values.
(x <- factor(c(1, 2, NA), exclude = NULL))  #INSTEAD OF NULL YOU CAN PUT NA
```


```{r}
is.na(x)[2] <- TRUE
x  # [1] 1    <NA> <NA>
```


```{r}
is.na(x)
# [1] FALSE  TRUE FALSE
```


```{r}
## More rational, since R 3.4.0 :
factor(c(1:2, NA), exclude =  "" ) # keeps <NA> , as
factor(c(1:2, NA), exclude = NULL) # always did
## exclude = <character>
z # ordered levels 'A < B < C'
factor(z, exclude = "C") # does exclude
factor(z, exclude = "B") # ditto
```


```{r}
## Now, labels maybe duplicated:
## factor() with duplicated labels allowing to "merge levels"
x <- c("Man", "Male", "Man", "Lady", "Female")
## Map from 4 different values to only two levels:
(xf <- factor(x, levels = c("Male", "Man" , "Lady",   "Female"),
                 labels = c("Male", "Male", "Female", "Female")))
#> [1] Male   Male   Male   Female Female
#> Levels: Male Female
```


```{r}
## Using addNA()
Month <- airquality$Month
table(addNA(Month))
table(Month)
```


```{r}
table(addNA(Month, ifany = TRUE))
# }






```


```{r}





```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
